---
title: "Bigger data"
subtitle: "with `arrow` and `duckdb`"
author: "Tom Mock & Edgar Ruiz"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: ["default", "css/my-theme.css", "css/my-fonts.css"]
    seal: false
    lib_dir: libs
    nature:
      ratio: '191:100'
      highlightStyle: dracula
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE,
        eval = TRUE)
library(tidyverse)
library(testthat)
library(arrow)
library(duckdb)
library(DBI)
library(gt)
library(devtools)
library(usethis)
```

```{r metathis, echo=FALSE}
library(metathis)
meta() %>%
  meta_name("github-repo" = "jthomasmock/bigger-data") %>% 
  meta_social(
    title = "Bigger data with arrow and duckdb",
    description = paste(
      "Bigger than memory data is easy to work with in R,",
      "and can be amazingly fast with arrow or duckdb!"
    ),
    url = "https://jthomasmock.github.io/bigger-data",
    image = "https://raw.githubusercontent.com/jthomasmock/bigger-data/master/images/title-card.png",
    image_alt = paste(
      "Title slide of 'Bigger Data with arrow and duckdb'.", 
      "A slide deck covering the basics of using arrow and duckdb with bigger than memory data.",
      "It also has a picture of two people walking up a large incline/mountain."
    ),
    og_type = "website",
    og_author = "Tom Mock",
    twitter_card_type = "summary_large_image",
    twitter_creator = "@thomas_mock",
    twitter_site = "@thomas_mock"
  )
```

class: title-slide, left, top

# `r rmarkdown::metadata$title`

## `r rmarkdown::metadata$subtitle`

### `r rmarkdown::metadata$author`

### `r Sys.Date()`

<br>

`r fontawesome::fa("link", "white")` [colorado.rstudio.com/rsc/bigger-data-prez](https://colorado.rstudio.com/rsc/bigger-data-prez)   
`r fontawesome::fa("github", "white")` [github.com/jthomasmock/bigger-data-prez](https://github.com/jthomasmock/bigger-data-prez)  

<span style='color:white;'>Slides released under</span> [CC-BY 2.0](https://creativecommons.org/licenses/by/2.0/)`r fontawesome::fa("creative-commons", "white")``r fontawesome::fa("creative-commons-by", "white")` ]   

<div style = "position: absolute;top: 0px;right: 0;"><img src="https://images.unsplash.com/photo-1579538800945-46d13c694a36?ixid=MnwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8&ixlib=rb-1.2.1&auto=format&fit=crop&w=1470&q=80" alt="Two people walking up a large mountain" width="600"></img></div>
